Introduction

### 2012-10-25 dissertation/tmpsolutions.tex
just the object lang
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@416 43ef1190-90fd-4dd7-a769-d0121f02b80e
w3c
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@417 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{verbatim}
</foo> void:propertyPartition 
  [
    void:property dct:language ;
    void:mostFrequentObjects lang:nb .
].
\end{verbatim}
This would declare \rdfterm{lang:nb} as the most frequent object for
\rdfterm{dct:language}, and this simple example would solve the
\langcase.

@@

I find the prospect of writing a first paper to explore these different
extensions to VoID very appealing. I would need to put down some
substantial work on notation, but not intending an very elaborate
theory, which is something that requires \SRL. The paper could discuss
the different approaches above, their merits and drawbacks. After
publishing, I could work with the W3C Semantic Web Interest Group to
get one of the solutions into VoID.

>>>>

\begin{verbatim}
</foo> void:propertyPartition 
  [
    void:property dct:language ;
    void:mostFrequentObjects lang:nb .
].
\end{verbatim}
This would declare \rdfterm{lang:nb} as the most frequent object for
\rdfterm{dct:language}, and so hint to the \fedeng that it should be
treated as having low selectivity. This simple example would solve the
\langcase.

@@

I find the prospect of writing a first paper to explore these different
extensions to VoID very appealing. I would need to put down some
substantial work on notation, but not intending an very elaborate
theory, which is something that requires \SRL. The paper could discuss
the different approaches above, their merits and drawbacks. After
publishing, I could work with the W3C Semantic Web Interest Group to
get one of the solutions into VoID (when we join the W3C).
